Tampering Detection In Low-Power Smart Cameras

### 2015-05-29 paper.tex
Aggiunta caption con AUC nelle ROC curves

\begin{figure}[t]
\centering
\subfigure[]{\label{fig:ROCdisplacement}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement}}
\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus}}
\caption{ROC curves for displacement detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean luma energy. \textbf{(b)} Analysis of the frame differencing.}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

\begin{figure}[t]
\centering
\subfigure[]{\label{fig:ROCdisplacement}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement}}
\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus}}
\caption{\textbf{(a)} ROC curve for displacement detection.
	There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	In particular, AUC of our solution is $0.9994$, while the solution which considers the whole image has an AUC of $0.9989$ and the one which considers Voronoi regions ha san AUC of $0.9985$.
	\textbf{(b)} ROC curve for blurring detection.
	In this case considering adaptive regions instead of considering the whole image is not convenient.
	In particular, AUC of the solution which considers adaptive regions is $0.9895$,  while the solution which considers the whole image has an AUC of $0.9996$}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
